\documentclass[8pt]{article}
\usepackage[a4paper]{geometry}

\title{Literature review: android studio.}
\author{ALVIN NSONGAMBI\\216004598\\16/u/10456PS}
\begin{document}
	\maketitle
	\pagenumbering{gobble}
\section{Abstract}
\paragraph{•}
for years Constant demand for IDEs and relatively easy way to write android programs without getting concerned with details of mobile compatibility  have been drawing developers into looking for the ideal IDE for android programs .google which is the official developer of the android operating system came up with one IDE that should be used with relative easy for android development..
\section{Introduction.}
\paragraph{•}
What is android studio?
According to the official android studio website \cite{developer.android.com - android developers}.
Android Studio is the official integrated development environment (IDE) for Google's Android operating system, built on JetBrains' IntelliJ IDEA software and designed specifically for Android development. It is available for download on Windows, macOS and Linux based operating systems. It is a replacement for the Eclipse Android Development Tools (ADT) as primary IDE for native Android application development.
The following documents are referenced in the given sections.
	\begin{itemize}
       \item Android Studio Release Notes
	   \item Download Options
	   \item Build Overview
	   \item Building Android Studio
	\end{itemize}
\section{Download Options}
\paragraph{•}
android studio can be downloaded and installed in various ways.
the web page here talked about various ways in which android studio can be download to a person computer.

Download Options \cite{download android studio and sdk tools | android studio}
here the website talked about the various ways in which android studio can be downloaded and installed to a computer.
It talked about the various system requirements need to install android studio for example 
Linux
GNOME or KDE desktop 
Tested on Ubuntu® 14.04 LTS, Trusty Tahr (64-bit distribution capable of running 32-bit applications)
64-bit distribution capable of running 32-bit applications 
GNU C Library (glibc) 2.19 or later 
3 GB RAM minimum, 8 GB RAM recommended; plus 1 GB for the Android Emulator 
2 GB of available disk space minimum,
4 GB Recommended (500 MB for IDE + 1.5 GB for Android SDK and emulator system image)
\section{terms and condtions}
\paragraph{•}
in this section the various terms and conditions for using android studio.
\subsection{•}
\cite{terms and conditions | android studio}
  The Android Software Development Kit (referred to in the License Agreement as the "SDK" and specifically including the Android system files, packaged APIs, and Google APIs add-ons) is licensed to you subject to the terms of the License Agreement. The License Agreement forms a legally binding contract between you and Google in relation to your use of the SDK.
\subsection{•}
"Android" means the Android software stack for devices, as made available under the Android Open Source Project, which is located at the following URL: http://source.android.com/, as updated from time to time.
\section{conclusion}
\paragraph{•}
Much as there are other IDEs such as eclipse that can be used for android development, android studio is the best for it is supported by the very developers of the android OS.
\bibliography{androidbib}
\bibliographystyle{plain}

\end{document}